\chapter{PyGTK 2.4 的新 widgets}
不少的新widgets和支持的对象被加入到PyGTK 2.4,包括以下内容:
• Action, RadioAction, ToggleAction - objects that represent actions that a user can take. Actions contain
information to be used to create proxy widgets ( for example, icons, menu items and toolbar items).
• ActionGroup - an object containing Actions that have some relationship, for example, actions to open, close
and print a document.
• Border - an object containing the values for a border.
• ColorButton - a button used to launch a ColorSelectionDialog.
• ComboBox - a widget providing a list of items to choose from. It replaces the OptionMenu.
• ComboBoxEntry - a widget providing a text entry field with a dropdown list of items to choose from. It replaces
the Combo.
• EntryCompletion - an object providing completion for an Entry widget.
• Expander - a container that can show and hide its child in response to its button click.
• FileChooser - an interface for choosing files.
• FileChooserWidget - a widget implementing the FileChooser interface. It replaces the
  FileSelection widget. 
• FileChooserDialog - a dialog used for "File/Open" and "File/Save" actions. It replaces the
    FileSelectionDialog. 
• FileFilter - an object used to filter files based on an internal set of rules.
• FontButton - a button that launches the FontSelectionDialog.
• IconInfo - an object containing information about an icon in an IconTheme.
• IconTheme - an object providing lookup of icons by name and size.
• ToolItem, ToolButton, RadioToolButton, SeparatorToolItem, ToggleToolButton - widgets
that can be added to a Toolbar. These replace the previous Toolbar items.
• TreeModelFilter - an object providing a powerful mechanism for revising the representation of an underlying
TreeModel. This is described in Section 14.10.2, “TreeModelFilter”.
• UIManager - 提供了一种从一个XML UI描述文件构建菜单和工具条的方式。它也有方法来管理多个UI描述文件的合并和拆分
\section{The Action and ActionGroup Objects}
	\subsection{Actions}
	\subsection{ActionGroup}
\section{ComboBox and ComboBoxEntry Widgets}
	\subsection{ComboBox Widgets}
	\subsection{ComboBoxEntry Widgets}
\section{ColorButton and FontButton Widgets}
	\subsection{ColorButton Widgets}
	\subsection{FontButton Widgets}
\section{EntryCompletion Objects}
\section{Expander Widgets}
\section{File Selection using FileChooser-based Widgets}
\section{The UIManager}
	\subsection{Overview}
	\subsection{Creating a UIManager}
	\subsection{Adding and Removing ActionGroups}
	\subsection{UI Descriptions}
	\subsection{Adding and Removing UI Descriptions}
	\subsection{Accessing UI Widgets}
	\subsection{A Simple UIManager Example}
	\subsection{Merging UI Descriptions}
	\subsection{UIManager Signals}
